### 2020-11-08 EPA_Census Team/Alison_Sociodemographic_Visualizations/Social_Demo_Chars_tidycensus.Rmd
Re-upload

Man_city_sex_age_acs5_2018 <- MI_sex_age_acs5_2018 %>%
  slice(18425:18471) %>%
  mutate(sex_age_label = sex_age_label) %>%
  select(sex_age_label, estimate)
```

>>>>

Man_city_sex_age_acs5_2018 <- MI_place_sex_age_acs5_2018 %>%
  slice(18425:18471) %>%
  mutate(sex_age_label = sex_age_label) %>%
  select(sex_age_label, estimate)
```
